Multiphysics Reactor-core Simulations Using the Improved Quasi-Static Method

### 2018-04-06 doc/Papers/IQS_convergence/IQS_convergence.tex

This work shows how effective IQS can be with different problem and time-discretization types. Possible future work would be to further optimize IQS for multi-physics problems in a more general sense. This proposed work would include an adaptation-like approach to the quasi-static evaluation of the non-neutronics physics. For instance, instead of a fixed number of temperature evaluations per macro step, adapting the number of these evaluations through the transient could improve results. This adaption could also be applied to other physics like thermal hydraulic and structural feedback.

>>>>

This work investigated the effectiveness of for several time discretizations. Extension to this work could include a further optimization of the IQS algorithm for multi-physics problems by extending, for instance,  the use of adaptivity in the evaluation of the other physic components. For example, instead of a fixed number of temperature evaluations per macro time-step, adapting the number of these evaluations during the transient could further reduce simulation times. This adaption could be applied to coupled physics such as thermal-hydraulic and structural feedback.
